Thoughts on resubmission within ARC1

### 2009-02-05 doc/client/client_technical.tex
Technical documentation update and mapping correction.

When addressing interoperability it is of paramount importance to
transparently address grid job descriptions written in different job
description languages by translating them automatically. In the
{\arclib} library this functionality is implemented in the
{\JobDescription} class. This is a generic class that takes a job
description (string) as input

\begin{shaded}
\begin{verbatim}
void setSource(const std::string source);
\end{verbatim}
\end{shaded}

in any supported formats (currently XRSL~\cite{xrsl}, JDL~\cite{jdl},
JSDL~\cite{jsdl}), converts and stores it in a JSDL-like internal job
description format. The identification of the source's description
format is internally handled by a \texttt{JobDescriptionOrderer} class
which identifies the format by pattern matching.

@@

\begin{shaded}
\begin{verbatim}
void getProduct(std::string& product, std::string format = "JSDL")
\end{verbatim}
\end{shaded}

The {\JobDescription} class has three back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern match
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and generating the job descriptions.

Parsing is currently possible from any of the languages but output
generation is only partially supported. Only JSDL and JDL output
generation is implemented yet and even for these there are some
limitations.

@@

Support for XRSL output generation is currently being developed.

>>>>

When addressing interoperability it is of paramount importance to
transparently address grid job descriptions written in different job
description languages by translating them automatically. In the
{\arclib} library this functionality is implemented in the
{\JobDescription} class. The inner representation (\texttt{JobInnerRepresentation}
class) is like to the GIN-JSDL and all elements are correspond to
variables. This variables are simple variables or complex data structures,
and private on the {\JobDescription} class.

This is a generic class that takes a job
description (string) as input

\begin{shaded}
\begin{verbatim}
bool setSource(const std::string source);
\end{verbatim}
\end{shaded}

in any supported formats (currently XRSL~\cite{xrsl}, JDL~\cite{jdl},
JSDL~\cite{jsdl}), converts and stores it in a GIN-JSDL-like internal job
description format. The identification of the source's description
format is internally handled by a \texttt{JobDescriptionOrderer} class
which identifies the format by pattern matching. If the source string is
empty or the \texttt{JobDescriptionOrderer} class can not be recognize
to any formats, then it is not store nothing and return with false, else
convert and store it.

@@

\begin{shaded}
\begin{verbatim}
bool getProduct(std::string& product, std::string format = "POSIXJSDL")
\end{verbatim}
\end{shaded}

The {\JobDescription} class has three back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern match
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and generating the job descriptions.
If the inner representation is empty or the source job descrition is not
valid, then the output is empty and return with false.
When the source format is equal with the output's format and it is not XRSL,
than set the product string with the source string. The XRSL output is
always generation from the inner representation.

Parsing is currently possible from any of the languages. JSDL, XRSL and
JDL output generation is implemented yet and even for these there are
some limitations.

@@
